Constraining Black Hole Growth with High-z Quasar Observations

### 2022-08-24 ms.tex
version0824; Sec5.1,5.2(fig only); Sec3.1 updated

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
key information on the physics determining the radiative and accretion processes of supermassive 
black holes (SMBHs) in high-redshift quasars.
Although the shape of the QLF has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor halos,
we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
in each of which constant Eddington ratio is assigned following a Schechter distribution function.
Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
suggests that several episodes of modest super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar surveys.
The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass
toward higher redshifts of $z>6$, compared to galaxy stellar mass.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
% the , Roman Space Telescope (RST), and Euclid.
\end{abstract}

@@

Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the QLF \citep[e.g.,][]{2017ApJ...847L..15O,2015ApJ...798...28K,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep[e.g.,][]{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
However, extrapolation of the Soltan argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
% applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in common regions in the early universe.
We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio is assigned 
following a Schechter distribution function. 
We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. 
Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
Furthermore, we construct the redshift-dependent QLF and BHMF that imply a rapid decay of 
their number and mass toward higher redshifts of $z>6$.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
Those results will be tested by future deep and wide-field surveys with the Roman Space Telescope and Euclid.

@@

Using the BHMF and its evolution, we construct the QLF, which can be directly probed by high-$z$ quasar observations.
%  compared with observations and in return constrain our model.
For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated by
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right),
\end{equation}
%
where we adopt a bolometric correction factor of $f^{\rm bol}_{1450}=4.4$ for the monochromatic UV band 
\citep{2006ApJS..166..470R}.
Combining this conversion factor and the ERDF to govern the BH growth, the quasar abundances with different luminosities 
can be constructed straightforwardly.
%Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
%the quasar abundances with different luminosities. 
However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
% a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
%it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
i.e., the number of fainter quasars observed as type-I AGNs is largely reduced by the obscuration effect
%Therefore, is the luminosity dependent obscuration fraction, 
%which decreases the fraction of the detectable quasars preferentially in the dimmer population 
\citep{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M}. 
%thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_LF.png}
\caption{
The quasar luminosity function at $z=6$ with the best-fit parameters (purple curve) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
%as described in \ref{fig:fitmf}. 
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
}
\label{fig:fitlf}
\end{figure*}

@@

\blue{
The best-fit parameters for the two cases of $\fseed$ both reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
The two parameters characterizing the ERDF are given as
$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075. 
The probability of rapid accretion in each cycle in the $\fseed=0.01$ case is slightly higher than that with $\fseed=0.1$,
while multiple accretion episodes enlarge the difference.
Moreover, given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
i.e., the ten-fold difference in $\fseed$ is nearly compensated.
%Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
%consistent with a general picture for the early assembly of SMBHs 
%\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
in the model would differ from those in observations.
On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to spend a larger fraction of time in active phases.
}

In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
reproduced by the best-fit parameters as well as the $1\sigma$ spread.
% where the QLF model excludes a contribution from obscured quasars, 
% yielding the {\it observed} QLF for type-I AGN populations.
The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
with statistical errors are also overlaid for comparison.
We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
$10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
Our best-fit BHMF model well agrees with their observational constraints in this mass range.
The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
% due to the lack of fine tuning by the model parameters in the low mass range, 
The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
Overall, the parameters are inferred to be reasonable fits consistent with the observational data.

@@

\subsection{Quasar luminosity function}

Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

@@

Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
we select quasars with a bolometric luminosity cut.
%of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$. 
In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue) and the selected sample with
a luminosity cut of $\Lbol \geq 10^{46}~\mathrm{erg~s^{-1}}$ (green) and $\Lbol \geq 10^{45}~\mathrm{erg~s^{-1}}$ (orange).  
The Eddington ratio for the whole sample follows a Schechter shape with a majority of inactive quasars, 
while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape. 
The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2022arXiv220705113F}.
However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
a large number of underlying BH populations with low Eddington ratios. 
%based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
We find that the log-normal shape still holds with the lower luminosity cut, 
%To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
%we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
but a lower detection limit unveils more hidden quasars with low Eddington ratios. 
This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
(Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
%Therefore, we emphasize that it is imperative to lower the detection limit in order to 
%understand a more complete quasar sample at high-$z$, 
%so that the numerous dimly accreting BHs can be shed light on.

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
key information on the physics determining the radiative and accretion processes of supermassive 
black holes (SMBHs) in high-redshift quasars.
Although the shape of the QLF has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor halos,
we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
in each of which constant Eddington ratio is assigned following a Schechter distribution function.
Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
suggests that several episodes of modest super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar surveys.
The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass
toward higher redshifts of $z>6$, compared to galaxy stellar mass.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
\end{abstract}

@@

Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2016ApJ...833..222J,2017ApJ...847L..15O,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep[e.g.,][]{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
However, extrapolation of the Soltan argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
% applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in common regions in the early universe.
We assume that the early BH population experiences multiple accretion bursts, in each of which constant Eddington ratio is assigned 
following a Schechter distribution function. 
We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced. 
Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
Furthermore, we construct the redshift-dependent QLF and BHMF that imply a rapid decay of 
their number and mass toward higher redshifts of $z>6$.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
by conducting spectroscopic measurements of individual BH masses and constructing high-$z$ QLFs.

@@

Using the BHMF and its evolution, we construct the QLF, which can be directly probed by high-$z$ quasar observations.
%  compared with observations and in return constrain our model.
For an accreting BH with a bolometric luminosity of $\Lbol=\lambda L_\mathrm{Edd}$, 
its rest-frame ultraviolot (UV) absolute magnitude of $\Muv$ at 1450 $\mathrm{\AA}$ is estimated by
%%%%%%%
%    Eq. 6
%%%%%%%
\begin{equation}
  \label{eq:M1450}
  \Muv= -21.0-2.5 \log  \left(\frac{\Lbol}{10^{45}~\mathrm{erg~s}^{-1}} \right) \rm{mag},
\end{equation}
%
where we adopt a bolometric correction factor of $f^{\rm bol}_{1450}=4.4$ for the monochromatic UV band 
\citep{2006ApJS..166..470R}.
Combining this conversion factor and the ERDF to govern the BH growth, the quasar abundances with different luminosities 
can be constructed straightforwardly.
%Under this conversion, an ERDF combined with the $z\sim$ 6 BH population is able to reproduce 
%the quasar abundances with different luminosities. 
However, we note that the shape and normalization of the {\it intrinsic} QLF is not necessary identical to the {\it observed} QLF
because quasar surveys with optical and near-infrared telescopes are not sensitive to the obscured quasar population at high redshifts,
% a larger fraction of fainter quasars are missed in current observations owing to quasar obscuration, 
%it is crucial to obtain we note that a vital ingredient to construct the observed QLF, 
i.e., the number of fainter quasars observed as type-I AGNs is largely reduced by the obscuration effect
%Therefore, is the luminosity dependent obscuration fraction, 
%which decreases the fraction of the detectable quasars preferentially in the dimmer population 
\citep{2003ApJ...598..886U,2007A&A...463...79G,2008A&A...490..905H,2014ApJ...786..104U,2014MNRAS.437.3550M}. 
%thus differs the normalization and shape of the observed QLF from the intrinsic one.

@@

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{fits_LF.png}
\caption{
The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
}
\label{fig:fitlf}
\end{figure*}

@@

\blue{
The best-fit parameters for the two cases of $\fseed$ both reproduce the bulk properties of the BHMF and QLF at $z\sim 6$,
despite in the $\fseed=0.01$ case the number of the whole BH population is ten times lower than that with $\fseed=0.1$.
The two parameters characterizing the ERDF are given as
$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075. 
The probability of rapid accretion in each cycle in the $\fseed=0.01$ case is slightly higher than that with $\fseed=0.1$,
while multiple accretion episodes enlarge the difference.
Moreover, given the best fit values of $\delta=(0.001,0.055)$ for the two $\fseed$ cases,
the higher $\delta$ value enhances the growth of small BHs with $M_\bullet <10^8~\Msun$ in the $\fseed=0.01$ case,
so that massive BHs are produced with number densities similar to that in the $\fseed=0.1$ case,
i.e., the ten-fold difference in $\fseed$ is nearly compensated.
The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
in the model would differ from those in observations.
On the other hand, the power-law index of $\alpha$ in the ERDF increases as the seeding fraction decreases,
indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
Thus, with lower seeding fractions, the high-$z$ quasar assembly ought to experience more active growth phases to reproduce the observations.
}

Next, we demonstrate that overall, the parameters are inferred to be reasonable fits consistent with the observational data of both of the BHMF and QLF.
In Fig.~\ref{fig:fitmf}, we show the total BHMF at $z=$ 6 reproduced by the best-fit parameters as well as the $1\sigma$ spread.
We also present the total BHMF indicated by \citetalias{2010AJ....140..546W} with statistical errors for comparison.
The BHMF data put more constraints in the fitting procedure, and help the fitting converge.
However, a complete BHMF is necessary for better constraints, especially the low-mass end, 
which inherit more of the seeding information during a short growth time.
For current comparison,
we note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
$10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
Our best-fit BHMF model well agrees with their constraints in this mass range.

The unobscured (type-I) QLF fitting results at $z=$ 6 are presented in Fig.~\ref{fig:fitlf},
along with the observed data from \citetalias{2018ApJ...869..150M}, which we adopt to the fitting.
The best-fit QLF results are consistent with observation over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$.
However, they overproduce the abundance of fainter quasars at $\Muv\gtrsim -24~{\rm mag}$,
reflecting both the less constraints from observational data in the faint end,
and the difficulty of reproducing such a small population of low-luminosity quasars based on our seeding and growth model.
The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
$-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
In \citet{2022NatAs...6..850J}, an upper limit of the faint end QLF is provided, % by non-detection of faint quasars
by analyzing this population in the Hubble Space Telescope (HST) imaging fields.
Our best-fit unobscured QLF results lie within their constraints.

On the other hand, studies on X-ray selected faint quasars report number densities much higher than that
extrapolated from rest-UV observations \citep{2015A&A...578A..83G,2019ApJ...884...19G}.
In addition to the systematic difference in the quasar identification methods,
the X-ray observation should suffer less dust obscuration (see \S~\ref{sec:LF}),
thus detect more quasars in the faint end.
We also show the intrinsic QLF predicted by our best-fit parameters,
which is without imposing obscuration thus representing the upper bound of detectable quasar numbers.
Our intrinsic QLF is broadly consistent with the faint-end QLF from X-ray observation,
despite slightly lower than their data points at $\Muv\gtrsim -21$ mag.
% outshining effect
From another point of view, studies explain the decrepancy of the UV and X-ray QLF in the faint end
by pointing out that only AGNs outshining their host galaxies can be identified by the point source criteria
in the rest-UV selection \citep{2020MNRAS.495.2135N,2022arXiv220712282K}.
Especially in the faint end at $\Muv\gtrsim -24$ mag, the galaxy population can potentially contribute to this contamination significantly 
\citep{2022ApJS..259...20H}.
We do not take into account of this effect in the QLF correction,
but we notice this important caveat and provide the galaxy number density information 
in the higher-$z$ QLF predictions (see \S~\ref{sec:qlfglf}).

% In Figs.~\ref{fig:fitmf} and \ref{fig:fitlf}, we show the total BHMF and unobscured (type-I) QLF at $z=$ 6 
% reproduced by the best-fit parameters as well as the $1\sigma$ spread.
% % where the QLF model excludes a contribution from obscured quasars, 
% % yielding the {\it observed} QLF for type-I AGN populations.
% The total BHMF indicated in \citetalias{2010AJ....140..546W} and QLF from \citetalias{2018ApJ...869..150M} 
% with statistical errors are also overlaid for comparison.
% We note that \citetalias{2010AJ....140..546W} constructed the BHMF using quasar samples with 
% $10^8~\Msun \lesssim \Mbh \lesssim 3\times 10^9~\Msun$.
% Our best-fit BHMF model well agrees with their observational constraints in this mass range.
% The QLF fitting results are also consistent with the observed one over $-29~{\rm mag} \lesssim \Muv \lesssim -25~{\rm mag}$,
% but seems to overproduce the abundance of fainter quasars at $\Muv>-24~{\rm mag}$.
% % due to the lack of fine tuning by the model parameters in the low mass range, 
% The difference at the fainter end tends to be alleviated with the seeding fraction lowered ($\fseed = 0.01$),
% because the progenitors of $z=6$ BHs with $10^{7-8}~\Msun$ (or similarly, 
% $-22~{\rm mag} \lesssim \Muv \lesssim -24~{\rm mag}$) were less massive seed BHs with $\sim 10^4~\Msun$,
% which is closer to the peak of the seed mass distribution (see Fig.~\ref{fig:seedmf}).
% Those BH population naturally produces a flatter slope of the QLF (and BHMF) at the faint (low-mass) end.
% Overall, the parameters are inferred to be reasonable fits consistent with the observational data.

@@

\subsection{Quasar luminosity function}
\label{sec:qlfglf}
Next, we show our prediction of $z=6-10$ unobscured QLFs taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution rises.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

@@

Based on the quasar sample from the best-fit model described in \S~\ref{sec:evol}, 
we select quasars with bolometric luminosity limits $L_{45}=10^{45}~\mathrm{erg~s^{-1}}$ and $L_{46}=10^{46}~\mathrm{erg~s^{-1}}$.
In Fig.~\ref{fig:lhist}, we present the intrinsic ERDFs for the whole BH sample (blue)
and the selected sample with a luminosity cut of $\Lbol \geq L_{45}$ (orange),
and $\Lbol \geq L_{46}$ (green).
For visible comparison, we elevate the observed histograms by a factor of 5 and 30
for the luminosity limits with $L_{45}$ and $L_{46}$, respectively.
The Eddington ratio for the whole sample follows a Schechter shape with a majority of inactive quasars, 
while the observed Eddington ratio is biased toward higher values and the distribution results in a log-normal shape. 
The latter distribution is presented by various observational efforts in the $z\sim$ 6 brightest quasar samples 
\citep[e.g.,][]{2010AJ....140..546W,2019ApJ...873...35S,2022arXiv220705113F}.
However, our best-fit growth model reproducing both the BHMF and QLF at $z\sim$ 6 suggests the existence of
a large number of underlying BH populations with low Eddington ratios. 
%based on the best-fit growth model connecting the BH seeding and $z\sim$ 6 BHMF and QLF. 
We find that the log-normal shape still holds with the lower luminosity cut, 
%To demonstrate qualitatively the caveat for the detection limit on recovering the intrinsic quasar properties, 
%we also examine the observed ERDF by selecting quasars with $\Lbol>10^{45}~\mathrm{erg~s^{-1}}$. 
but a lower detection limit unveils more hidden quasars with low Eddington ratios. 
This will be proved by the ongoing observations with the Subaru HSC providing low-luminosity and less-massive BH samples
(Onoue et al. in prep) and upcoming optical survey by the Vera C. Rubin Observatory.
%Therefore, we emphasize that it is imperative to lower the detection limit in order to 
%understand a more complete quasar sample at high-$z$, 
%so that the numerous dimly accreting BHs can be shed light on.
